\documentclass[11pt]{article}

%\usepackage{palatino}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}
\newcommand{\cellone}{3.5cm} %% 2.5cm
\newcommand{\celltwo}{11cm}
\newcommand{\cellthree}{4cm}

\newcommand{\incellone}{3cm}
\newcommand{\incelltwo}{5cm}
\newcommand{\incellthree}{10cm}
\newcommand{\latex}{\LaTeX}
\newcommand{\spa}{\vspace{.4in}}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={210mm,297mm},
 left=7mm,
 right=10mm,
 top=15mm,
 bottom=20mm,
 }


\begin{document}


{\huge Andrew J. Basinski \hspace{2.5in} January, 2022}

\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

\spa

\begin{tabularx}{\textwidth}{p{\incellone} p{\incelltwo} p{\incellthree}}

  C\textsc{ontact} & \parbox[t]{5 cm}{Andrew Basinski \\ Stevens Point, WI 54481} & \parbox[t]{8cm}{%%Phone: \\%%715-252-XXXX\\
%%    Email: \\%%abasinski@uidaho.edu \\
    Website: \url{https://54481andrew.github.io/}
  } \\

\end{tabularx}

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
E\textsc{ducation} & \parbox[t]{\celltwo}{{\bf Ph.D., Mathematics} University of Utah \\  \emph{Adviser: Dr. Frederick Adler}} &  August, 2016 \\[.5in]   

		          & \parbox[t][0cm]{13cm}{{\bf B.S., Biology} University of Wisconsin-Stevens Point} & Spring, 2009 \\
		          & \parbox[t]{13cm}{{\bf B.S., Mathematics} University of Wisconsin-Stevens Point} & Spring, 2009 \\
\end{tabularx} 

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
  \parbox[t][0cm]{\cellone}{A\textsc{ppointments}}  & \parbox[t]{10cm}{Computational Data Scientist. Institute for \\Interdisciplinary Data Sciences, University of Idaho, Moscow, ID 83844} & \parbox[t][]{\cellthree}{December, 2021 - \\ Present}
\end{tabularx}

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
  \parbox[t][0cm]{\cellone}{}  & \parbox[t]{10cm}{Post-Doctoral Associate with Chris Remien and Scott \\ Nuismer. Department of Mathematics, University of Idaho, Moscow, ID 83844} & \parbox[t][]{\cellthree}{October, 2016 - \\ November, 2021}
\end{tabularx}

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo}}
  \parbox[t][0cm]{\cellone}{R\textsc{esearch} E\textsc{xperience}} & \parbox[t][0cm]{12cm}{
    Disease forecasting models, machine learning, machine vision with convolutional neural networks, epidemiological models, spatial ecology, ODE and PDE numerical simulation and analysis, stochastic models, agent-based simulation}
\end{tabularx}

\spa
\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo}}
  \parbox[t][0cm]{\cellone}{P\textsc{ublications}} &  \parbox[t][0cm]{12cm}{ 

    \vspace{-0.65cm}
    \begin{itemize}
      
    \item Varrelman TJ, Remien CH, {\bf Basinski AJ}, et al.
      Quantifying the effectiveness of betaherpesvirus-vectored
      transmissible vaccines. \emph{Proceedings of the National Academy of
        Sciences} 119.4 (2022)
      
    \item {\bf Basinski AJ}, Fichet-Calvet EJ, Sjodin AR, et
      al. Bridging the gap: Using reservoir ecology and human
      sero-surveys to estimate Lassa incidence in West
      Africa. \emph{PLoS Computational Biology} 17.3 (2021).

      \vspace{0.05in}      

    \item Layman NC, Tuschhoff BM, {\bf Basinski AJ}, et
      al. Suppressing evolution in genetically engineered systems
      through repeated supplementation. \emph{Evolutionary
      Applications} 14.2 (2020).
      
      \vspace{0.05in}
      
    \item Schreiner CL, Nuismer SL, {\bf Basinski AJ}. When to
      vaccinate a fluctuating wildlife population: is timing
      everything? \emph{Journal of Applied Ecology} 57.2 (2020).

      \vspace{0.05in}      
      
    \item Nuismer SL, Remien CH, {\bf Basinski AJ}, et al. Bayesian
      estimation of Lassa virus epidemiological parameters:
      implications for spillover prevention using wildlife
      vaccination. \emph{PLoS Neglected Tropical Diseases} 14.9
      (2020).
      
    \end{itemize}
  }
\end{tabularx}

\newpage

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo}}
  \parbox[t][0cm]{\cellone}{P\textsc{ublications}
    \\ \textsc{(Continued)}} & \parbox[t][0cm]{12cm}{

    \vspace{-0.65cm}
    \begin{itemize}


      
    \item {\bf Basinski AJ}, Nuismer SL, Remien CH. A little goes a
      long way: Weak vaccine transmission facilitates oral vaccination
      campaigns against zoonotic pathogens. \emph{PLoS Neglected
      Tropical Diseases} 13.3 (2019).

      \vspace{0.05in}

      \item Smithson MW, {\bf Basinski AJ}, Nuismer SL, Bull
        JJ. Transmissible vaccines whose dissemination rates vary
        through time, with applications to wildlife. \emph{Vaccine}
        37.9 (2019).

      \vspace{0.05in}
        

    \item Varrelman TJ, {\bf Basinski AJ}, Remien CH, Nuismer
      SL. Transmissible vaccines in heterogeneous populations:
      Implications for vaccine design. \emph{One Health} 7 (2019).

      \vspace{0.05in}
      
    \item Nuismer SL, May RH, {\bf Basinski AJ}, Remien
      CH. Controlling epidemics with transmissible
      vaccines. \emph{PloS One} 13.5 (2018).
      
      \vspace{0.05in}
      
    \item {\bf Basinski AJ}, Varrelman TJ, Smithson MW, et
      al. Evaluating the promise of recombinant transmissible
      vaccines. \emph{Vaccine} 36.5 (2018).
      
    \end{itemize}
  }
\end{tabularx}

\spa
\spa
\spa
\spa
\spa
\spa
\spa
\spa
\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
  \parbox[t][0cm]{\cellone}{P\textsc{resentations}}  & \parbox[t][]{\celltwo}{{\bf Univ. Idaho Math Colloquium}, Moscow, ID, US} & \parbox[t][]{\cellthree}{Feb., 2021} \\ 
  & \hspace{.2in} \parbox[t][]{\celltwo}{ \emph{Talk: } Using mathematics and machine learning \\to
guide the control of human pathogens in
wildlife} \\

  & \vspace{0.1in} \parbox[t][]{\celltwo}{{\bf MIDAS Meeting}, Washington DC, US} & \vspace{0.1in} \parbox[t][]{\cellthree}{April, 2018} \\ 
  & \hspace{.2in} \parbox[t][]{\celltwo}{ \emph{Talk: } The benefits and challenges of using transmissible \\
  vaccines in zoonotic vaccination campaigns} \\

  & \vspace{0.1in} \parbox[t][]{\celltwo}{{\bf Society for Mathematical Biology}, SLC, UT, US} & \vspace{0.1in} \parbox[t][]{\cellthree}{July, 2017} \\ 
  & \hspace{.2in} \parbox[t][]{\celltwo}{ \emph{Poster: } Evaluating the Promise of Recombinant \\ Transmissible Vaccines} \\

  
  & \vspace{0.1in} \parbox[t][]{\celltwo}{{\bf Science Day}, SLC, UT, US} & \vspace{0.1in} \parbox[t][]{\cellthree}{Nov., 2013/2014} \\ 
  & \hspace{.2in} \parbox[t][]{\celltwo}{ \emph{Talk: } Can Ants Do Calculus?}\\
  
  
  & \vspace{0.1in} \parbox[t][]{\celltwo}{{\bf Society for Mathematical Biology}, Tempe, AZ, US} & \vspace{0.1in} \parbox[t][]{\cellthree}{June, 2014} \\ 
  & \hspace{.2in} \parbox[t][]{\celltwo}{ \emph{Talk: } The effects of colony structure on resource \\ collection ability} \\
  
											 
  & \vspace{0.1in} \parbox[t][0cm]{\celltwo}{{\bf Univ. Utah Biology Retreat}, SLC, UT, US } & \vspace{0.1in} \parbox[t][]{\cellthree}{Oct., 2013} \\
  & \hspace{.2in} \parbox[t][]{\celltwo}{\emph{Poster:} The Consequences of Owning Multiple Homes: \\ Polydomy in Ants}
\end{tabularx}

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
\parbox[t][0cm]{\cellone}{S\textsc{cientific} C\textsc{omputing}} & \parbox[t][0cm]{\celltwo}{R, Python, Github, Mathematica, C++, \latex, Linux systems} 
\end{tabularx}

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}

\parbox[t][0cm]{\cellone}{T\textsc{eaching} E\textsc{xperience}} &  \parbox[t][0cm]{\celltwo}{{\bf  Math In Medicine} (Math 4600)}  &  Spring, 2015 \\ 
					          &  \parbox[t][0cm]{\celltwo}{{\bf  Calculus III} (Math 2210)} &  Fall, 2014 \\
					          &  \parbox[t]{\celltwo}{{\bf Glendale Middle School} Advanced Science}   &  \parbox[t]{\cellthree}{Fall, 2011 - Spr., 2012} \\				
					          &  \parbox[t]{\celltwo}{{\bf Calculus I} (Math 1210)}   &  \parbox[t]{\cellthree}{Fall, 2010} \\					          
					          &  \parbox[t]{\celltwo}{{\bf  Business Calculus} (Math 1210)}   &  \parbox[t]{\cellthree}{Spr., 2011, Spr., 2010 \\ Fall, 2009 }

\end{tabularx}

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
  
  \parbox[t][0cm]{\cellone}{T\textsc{eaching} A\textsc{ssistant} E\textsc{xperience}} & \parbox[t][0cm]{\celltwo}{{\bf  Calculus II} (Math 1320)}  &  \parbox[t][]{\cellthree}{Spring, 2016}\\ 
  
  
  & \parbox[t][0cm]{\celltwo}{{\bf  PDE's for Engineers} (Math 3140)}  &  \parbox[t][]{\cellthree}{Fall, 2015}\\ 
  
  &  \parbox[t][0cm]{\celltwo}{{\bf  Math in Medicine} (Math 4600)}  &  \parbox[t][]{\cellthree}{Spr., 2013, Spr., 2014}\\  
  &  \parbox[t][0cm]{\celltwo}{{\bf  Math Models In Biol} (Biol 5910)}  &  \parbox[t][]{\cellthree}{Fall, 2013} \\ 					          
  &  \parbox[t][1cm]{\celltwo}{{\bf  Math Biology I} (Math 5110)}  &  Fall, 2012 
\end{tabularx}

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
  \parbox[t][0cm]{\cellone}{S\textsc{tudent} R\textsc{easearch}} & \parbox[t][]{\celltwo}{Mentor for Courtney Schreiner (wildlife vaccination)} & \parbox[t][0cm]{\cellthree}{2018-} 

\end{tabularx}

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
\parbox[t][0cm]{\cellone}{A\textsc{wards}, H\textsc{onors}, F\textsc{ellowships}} & \parbox[t][0cm]{\celltwo}{{\bf Graduate Teaching Fellowship}, Mathematics} & \parbox[t][]{\cellthree}{Fall, 2009 - Spr., 2011 \\ Fall, 2014 - 2016} \\ 
												        & \parbox[t][0cm]{\celltwo}{{\bf RTG Teaching Fellowship} in Math. Biology} & \parbox[t][]{\cellthree}{Fall, 2012 - Spr., 2014} \\
												        &  \parbox[t][0cm]{\celltwo}{{\bf SCIF Grant}}  &  Summer, 2012 \\ 	
												        &  \parbox[t][0cm]{\celltwo}{{\bf WEST Fellowship}}  &  Fall, 2011 - Spr., 2012 \\ 
\end{tabularx}

\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
\parbox[t][]{\cellone}{A\textsc{cademic} S\textsc{ervice}} & \parbox[t][0cm]{\celltwo}{{\bf Journal Reviews} for Oecologia, PLOS ONE, Journal of Theoretical Biology.  F1000 member. } & \parbox[t][]{\cellthree}{2013 - 2016} \\ \\
                                                                                                      & \parbox[t][0cm]{\celltwo}{Designed and ran Society of Math Biology booth at {\bf USA Science and Engineering Festival} in Washington D.C.} & \parbox[t][]{\cellthree}{April, 2014} 

\end{tabularx}

\spa
%%\spa

\begin{tabularx}{\textwidth}{p{\cellone} p{\celltwo} p{\cellthree}}
  \parbox[t][0cm]{\cellone}{R\textsc{eferences}} & \parbox[t][0cm]{6cm}{
    \vspace{-0.65cm}


    
%%     \begin{itemize}
%%     \item \parbox[t]{10cm}{Dr. Christopher Remien (cremien@uidaho.edu) \\ Office phone: (208) 885-5901 \\ Mathematics, University of Idaho}
%%     \item \parbox[t]{10cm}{Dr. Scott Nuismer (snuismer@uidaho.edu)  \\ Office phone: (208) 596-1949   \\ Biology, University of Idaho}
%%     \item \parbox[t]{10cm}{Dr. Jim Bull (jbull@uidaho.edu) \\ Office phone: (512)-618-9892 \\ Biology, University of Idaho}
%%     \item \parbox[t]{10cm}{Dr. Paul Gessler (paulg@uidaho.edu) \\ Office phone: (208) 310-2942 \\ Natural Resources (GIS), University of Idaho}      
%% %    \item \parbox[t]{10cm}{Dr. Frederick Adler (adler@math.utah.edu) \\ Office phone (biology): (801) 581-6848 \\ Office phone (math): (801) 585-6202 \\ Biology and Mathematics, University of Utah}
%%     \end{itemize}
   }
  
\end{tabularx}

\center Available upon request
\end{document}
